DINO Methods for Style Transfer

### 2022-04-19 paper/Paper.tex
conclusion

>>>>

In this paper we have shown that the transformers already trained using DINO are very useful, and we used them to achieve strong style transfer results. We also saw that this training method is very sensitive, and difficult to apply to new contexts. In future we hope to see attempts to apply this training method to other areas of computer vision, and we also hope to gain more theoretical understanding of why DINO works in some scenarios, but fails in others.
